Active Object Search with a Mobile Device for the Visually Impaired

### 2018-12-22 paper.tex

\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments that determined how effective the system is at directing a participant to point the device's camera towards a target object. This section discusses the experiments and their results.

>>>>

\noindent To test the effectiveness of our MDP and its policies, we designed a set of experiments to determine how effective the system is at guiding the participant in pointing the camera towards a target object. This section presents the experiments and following results.
